### 2011-06-19 manuscript.tex
Add title page, licensing, etc.  Submitted this for review (Createspace).

\documentclass[12pt]{book}
\usepackage[paperwidth=5.25in,paperheight=8in,hmargin=0.75in,vmargin=0.5in]{geometry}

@@

\begin{document}

>>>>

\documentclass[12pt]{book}
\usepackage[paperwidth=5.25in,paperheight=8in,hmargin=0.75in,vmargin=0.5in]{geometry}
\usepackage{url}

@@

\begin{document}
\thispagestyle{empty}
~\\
\vspace{2in}
\begin{center}
\LARGE{ESCAPE VELOCITY}

\vspace{1in}
\large{Adam C. Jensen}
\end{center}

\newpage

{\small
\noindent This book is licensed under a Creative Commons \\Attribution-Noncommercial-ShareAlike license, which lets you share it, remix it, and share your remixes, provided that you do so on a noncommercial basis.

For more information please visit the following URL:

\noindent \url{http://creativecommons.org/licenses/by-nc-sa/3.0/}

The most recent version of this book is always available on my website at \url{http://linuxguy.org} .

~\\
\noindent ISBN-13: 978-1463548353

\noindent ISBN-10: 1463548354
}
